### 2020-07-21 paper/cover-letter/cover-letter.tex
Minor changes

		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Dr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, and Prof. Kathryn D. Huff) are submitting for exclusive consideration of publication as a research article in Annals of Nuclear Energy. The current manuscript introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR. This paper focuses on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady state.

>>>>

		Please find enclosed a manuscript entitled: ``Preliminary design of control rods in the single-fluid double-zone thorium molten salt reactor (SD-TMSR)'' which I and my coauthors (Dr. Andrei Rykhlevskii, Prof. G. V. Tikhomirov, and Prof. Kathryn D. Huff) are submitting for exclusive consideration of publication as a research article in Annals of Nuclear Energy. The current manuscript introduces a reliable safety system based on control rods in addition to the online feed system reactivity control in the SD-TMSR. This paper focuses on control rod design and material selection, integral and differential control rod worth, shutdown margin, and shadowing effects at steady-state.
